A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
updated figures from the parameter search experiments

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range \dean{([-3.29,3.77]~mV)}. The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/RMSESensor.pdf}
\end{center}
\caption{{\bf RMSE of the kernel estimates}. RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$. Mean kernel estimates are obtained over 50 realisations in each case.}
\label{fig:Figure13}
\end{figure*}
\section*{Tables}

>>>>

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 10.73~\% of the field voltage range ([-2.20,2.46]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/RMSESensor.pdf}
\end{center}
\caption{{\bf RMSE of the kernel estimates}. RMSE of the kernel for different values of sensor width, $\sigma_m$, distance between adjacent sensors is $\Delta_y=1.5$. Mean kernel estimates are obtained over 50 realisations in each case.}
\label{fig:Figure13}
\end{figure*}
\section*{Tables}
